---
title: "Homework_Week_4_Part_2"
author: "Arora"
date: "September 30, 2017"
output: html_document
---

```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
###Problem 1: Calculate the population mean and standard deviation for the following variables: height, weight, age, number of zombies killed and years of education. 

```{r}
data(d)
d

#Height
m<-mean(d$height)
m

j<-d$height

pop_v <- function(j) {
    sum((j - mean(j))^2)/(length(j))
}
pop_v(j)
sqrt(pop_v(j))

#Weight
m<-mean(d[,6])
m

j<-d$weight

pop_v <- function(j) {
    sum((j - mean(j))^2)/(length(j))
}
pop_v(j)
sqrt(pop_v(j))


#Age
m<-mean(d[,10])
m

j<-d$age

pop_v <- function(j) {
    sum((j - mean(j))^2)/(length(j))
}
pop_v(j)
sqrt(pop_v(j))

#Number of Zombies Killed
m<-mean(d[,7])
m

j<-d$zombies_killed

pop_v <- function(j) {
    sum((j - mean(j))^2)/(length(j))
}
pop_v(j)
sqrt(pop_v(j))

#Years of Education
m<-mean(d[,8])
m

j<-d$years_of_education

pop_v <- function(j) {
    sum((j - mean(j))^2)/(length(j))
}
pop_v(j)
sqrt(pop_v(j))
```
###Problem 2
###ggplot boxplots of gender versus (height, weight, age, number of zombies killed, and years of education)

```{r}
#Plot for Height
library(ggplot2)
p <- ggplot(data = d, aes(x = gender, y = height))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("height")
p
```
```{r}
#Plot for Weight
p <- ggplot(data = d, aes(x = gender, y = weight))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("weight")
p
```

```{r}
#Plot for Age
p <- ggplot(data = d, aes(x = gender, y = age))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("age")
p
```

```{r}
#Plot for Number of Zombies Killed
p <- ggplot(data = d, aes(x = gender, y = zombies_killed))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("Number of Zombies Killed")
p
```

```{r}
#Plot for Years of Education
p <- ggplot(data = d, aes(x = gender, y = years_of_education))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("Years of Education")
p
```

###Problem 3
###Time to make the scatterplots of gender versus (height, weight, age,)
```{r}
#Scatterplot for Age versus Height

     
p <- ggplot(data = d, aes(x = age, y = height))  # first, we build a plot object and color points by Family
p <- p + xlab("Age") + ylab("Height")  # then we modify the axis labels
p <- p + geom_point()  # then we make a scatterplot
p <- p + theme(legend.position = "bottom", legend.title = element_blank())  # then we modify the legend
p  # and, finally, we plot the object
```
Show in New WindowClear OutputExpand/Collapse Output

Show in New WindowClear OutputExpand/Collapse Output


```{r}
#Scatterplot for Age versus Weight
p <- ggplot(data = d, aes(x = age, y = weight))  # first, we build a plot object and color points by Family
p <- p + xlab("Age") + ylab("Weight")  # then we modify the axis labels
p <- p + geom_point()  # then we make a scatterplot
p <- p + theme(legend.position = "bottom", legend.title = element_blank())  # then we modify the legend
p  # and, finally, we plot the object
```

###For both there seems to be a linear correlation however there seems to be a larger correlation for height than for weight

###Problem 4
###Q-Q Historgrams and Looking for Normality
```{r}
qqnorm(d$height, main="Normal QQ plot for Height")
qqline(d$height, col="blue")
hist(d$height, breaks = seq(from = 50, to = 100, by = 5), probability = TRUE)
#This is a normal distribution

qqnorm(d$weight, main="Normal QQ plot for Height")
qqline(d$weight, col="blue")
hist(d$weight, breaks = seq(from = 80, to = 220, x=1), probability = TRUE)
#This is a normal distribution

qqnorm(d$age, main="Normal QQ plot for Age")
qqline(d$age, col="blue")
hist(d$age, breaks = seq(from = 0, to = 30, x = 1))
#This is a normal distribution

qqnorm(d$zombies_killed, main="Normal QQ plot for Number of Zombies Killed")
qqline(d$zombies_killed, col="blue")
hist(d$zombies_killed, breaks = seq(from = 0, to = 15, x = 1))
#This is a Poisson distribution therefore the qqnorm plots are not valid

qqnorm(d$years_of_education, main="Normal QQ plot for Years of Education")
qqline(d$years_of_education, col="blue")
hist(d$years_of_education, breaks = seq(from = 0, to = 10, x = 1))
#This is also a Poisson distribution therefore the qqnorm are not valid
```

###Problem 5
### Using sample() to gain a single subset of 30 zombie survivers and calculating the mean and standard deviation for each of the following varaibles (height, weight, age, years of education, number of zombies killed)

```{r}
s<-d[sample(nrow(d), 30), ]
s
n<-30

m<-mean(s$height)
m
v<-var(s$height)
v
sigma<-sqrt(v)
sigma
e <- sqrt(v/n)

upper<-m+qnorm(0.95, mean=m, sd=sigma)*e
upper
lower<-qnorm(0.05, mean=m, sd=sigma)*e
lower

mean(s$weight)
m
v<-var(s$weight)
v
sigma<-sqrt(v)
sigma
e <- sqrt(v/n)

upper<-m+qnorm(0.95, mean=m, sd=sigma)*e
upper
lower<-qnorm(0.05, mean=m, sd=sigma)*e
lower

mean(s$age)
m
v<-var(s$age)
v
sigma<-sqrt(v)
sigma
e <- sqrt(v/n)

upper<-m+qnorm(0.95, mean=m, sd=sigma)*e
upper
lower<-qnorm(0.05, mean=m, sd=sigma)*e
lower

mean(s$zombies_killed)
v<-var(s$zombies_killed)
v
sigma<-sqrt(v)
sigma
#lambda is equal to the number of zombies killed over the number of people killing zombies
#therefore lambda is equal to sum(s$zombies_killed)/30
lambda<-sum(s$zombies_killed)/length(s)
lambda
standard_error<-sqrt(lambda/length(s))
standard_error
#confidence interval is lambda +/-1.96(standard_error); the 1.96 means that 1.96 standard deviations from the mean fall under 95% of the normal curve. I think this means that this is a type of normal approximation, but I could find no other way of creating a confidence interval for a Poisson distribution. 
upper<-lambda+1.96*(standard_error)
upper
lambda-1.96*(standard_error)
lower


mean(s$years_of_education)
m
v<-var(s$years_of_education)
v
sigma<-sqrt(v)
sigma
lambda<-sum(s$years_of_education)/length(s)
lambda
standard_error<-sqrt(lambda/length(s))
standard_error
#confidence interval is lambda +/-1.96(standard_error)
upper<-lambda+1.96*(standard_error)
upper
lambda-1.96*(standard_error)
lower
```
###Problem 6
###This is where 99 additional samples are drawn and the mean for each variable is calculated for each sample (that's 5 variables times 99 additional samples). The standard deviations are also calculated. Then discuss what the sampling distributions look like. 


###For Height
```{r}
x <- d$height
m <- mean(x)
v <- var(x)/(1000-1)
stdv <- sqrt(v)


#And then from above I would set up the variable to calculate 99 iterations?

set <- NULL  # sets up a dummy variable to hold our  simulations
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(x, n, replace = TRUE))
}

s<-d[sample(nrow(d), 30), ]
s

m<-mean(s$height)
m

#b is the mean of the all 100 samples
b<-(99*(mean(set))+1*mean(s$height))/100
b
#g is the new standard deviation of both s and set which I took by combining the new variances into j. I think it would be a lot easier to just run 100 simulations than trying to combine; the combination of the variances should work because it follows the variance sum law because both are independent. 
 j<-var(s$height)+var(set)
j
g<-sqrt(j)
g
qqnorm(set, main="Normal QQ plot for Height")
qqline(set, col="blue")
hist(set)
```

#For Weight
```{r}
x <- d$weight
m <- mean(x)
v <- var(x)/(1000-1)
stdv <- sqrt(v)


#And then from above I would set up the variable to calculate 99 iterations?

set <- NULL  # sets up a dummy variable to hold our  simulations
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(x, n, replace = TRUE))
}

s<-d[sample(nrow(d), 30), ]
s

m<-mean(s$weight)
m

#b is the mean of the all 100 samples
b<-(99*(mean(set))+1*mean(s$weight))/100
b
#j is the combination of the variance and g is the standard deviation
j<-var(s$height)+var(set)
j
#j is the variance 
g<-sqrt(j)
g

qqnorm(set, main="Normal QQ plot for Weight")
qqline(set, col="blue")
hist(set)
```

#For Age
```{r}
x <- d$age
m <- mean(x)
v <- var(x)/(1000-1)
stdv <- sqrt(v)


#And then from above I would set up the variable to calculate 99 iterations?

set <- NULL  # sets up a dummy variable to hold our  simulations
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(x, n, replace = TRUE))
}

s<-d[sample(nrow(d), 30), ]
s

m<-mean(s$age)
m

#b is the mean of the all 100 samples
b<-(99*(mean(set))+1*mean(s$age))/100
b
#j is the combination of the variance and g is the standard deviation
j<-var(s$age)+var(set)
j
#j is the variance 
g<-sqrt(j)
g

qqnorm(set, main="Normal QQ plot for Age")
qqline(set, col="blue")
hist(set)
```

#For Number of Zombies Killed
```{r}
x <- d$zombies_killed
m <- mean(x)
v <- var(x)/(1000-1)
stdv <- sqrt(v)


#And then from above I would set up the variable to calculate 99 iterations?

set <- NULL  # sets up a dummy variable to hold our  simulations
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(x, n, replace = TRUE))
}

s<-d[sample(nrow(d), 30), ]
s

m<-mean(s$zombies_killed)
m

#b is the mean of the all 100 samples
b<-(99*(mean(set))+1*mean(s$zombies_killed))/100
b
#j is the combination of the variance and g is the standard deviation
j<-var(s$zombies_killed)+var(set)
j
#j is the variance 
g<-sqrt(j)
g

qqnorm(set, main="Normal QQ plot for Number of Zombies Killed")
qqline(set, col="blue")
hist(set)
```

#For Years of Education
```{r}
x <- d$years_of_education
m <- mean(x)
v <- var(x)/(1000-1)
stdv <- sqrt(v)


#And then from above I would set up the variable to calculate 99 iterations?

set <- NULL  # sets up a dummy variable to hold our  simulations
n <- 30
for (i in 1:99) {
    set[i] <- mean(sample(x, n, replace = TRUE))
}

s<-d[sample(nrow(d), 30), ]
s

m<-mean(s$years_of_education)
m

#b is the mean of the all 100 samples
b<-(99*(mean(set))+1*mean(s$years_of_education))/100
b
 
j<-var(s$years_of_education)+var(set)
j
#j is the combination of the variance and g is the standard deviation
g<-sqrt(j)
g
qqnorm(set, main="Normal QQ plot for Years of Education")
qqline(set, col="blue")
hist(set)
```
#Answers for Questions in Problem 6
####The means and standard deviations when I calculated them last are as follows: Height, mean = 67.55852, sigma = 4.451259; the standard error for height in #5 is 0.9201227 which is far off from the standard deviation which either means there is an issue with the code or that the standard error from the sample does not reflect the standard deviation of the population. 

####For Weight, mean = 143.6187, and sigma = 5.631403. The standard error is 3.651578 whic his closer than for height. 

#### For age mean = 20.13286, and sigma = 3.153109. The standard error is 0.5368274. 

####For Number of Zombies Killed, mean = 2.833333, and sigma = 2.087845. The standard error is 1.019804. This is not close to sigma either. 

####And for Years of Education, mean = 2.973, and 1.743745. The standard error is 0.8831761. This last value is also not close to the standard deviation and again I'm inclined to think that the more samples taken the more likely the values of mean and standard deviation will reflect the true population. 

####Every sampling distribution looked varily normal. However for the ones taken from a population with a normal distribution (height, weight, and age), the sample distributions looked less normal. For the variables from the populations not normally distributed (Poisson distributions were for years of education and number of zombies killed), the sampling distribution looks more normal. This could either be an error in my code, or it could be the issue with bootstrapping. I've been reading that is is not applicable to every situtation and something in my code may have caused bootstrapping to not be a useful tool in sampling this population. 
