---
title: "Homework_Week_4_Part_2"
author: "Arora"
date: "September 30, 2017"
output: html_document
---

```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
#Problem 1: Calculate the population mean and standard deviation for the following variables: height, weight, age, number of zombies killed and years of education. 

```{r}
data(d)

#Height
m<-mean(d[,5])
m
v<-var(d[,5])*(999/1000)
v
s<-sqrt(v)
s

#Weight
m<-mean(d[,6])
m
v<-var(d[,6])*(999/1000)
v
s<-sqrt(v)
s

#Age
m<-mean(d[,10])
m
v<-var(d[,10])*(999/1000)
v
s<-sqrt(v)
s

#Number of Zombies Killed
m<-mean(d[,7])
m
v<-var(d[,7])*(999/1000)
v
s<-sqrt(v)
s

#Years of Education
m<-mean(d[,8])
m
v<-var(d[,8])*(999/1000)
v
s<-sqrt(v)
s
```
#Problem 2
#ggplot boxplots of gender versus (height, weight, age, number of zombies killed, and years of education)

```{r}
#Plot for Height
library(ggplot2)
p <- ggplot(data = d, aes(x = gender, y = height))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("height")
p
```
```{r}
#Plot for Weight
p <- ggplot(data = d, aes(x = gender, y = weight))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("weight")
p
```

```{r}
#Plot for Age
p <- ggplot(data = d, aes(x = gender, y = age))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("age")
p
```

```{r}
#Plot for Number of Zombies Killed
p <- ggplot(data = d, aes(x = gender, y = zombies_killed))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("Number of Zombies Killed")
p
```

```{r}
#Plot for Years of Education
p <- ggplot(data = d, aes(x = gender, y = years_of_education))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("Years of Education")
p
```

#Problem 3
#Time to make the scatterplots of gender versus (height, weight, age, number of zombies killed, and years of education)
```{r}
#Scatterplot for Gender versus Height
p <- ggplot(data = d, aes(x = gender, y = height, 
    color = factor(gender)))  # first, we build a plot object and color points by Family
p <- p + xlab("Gender") + ylab("Height")  # then we modify the axis labels
p <- p + geom_point()  # then we make a scatterplot
p <- p + theme(legend.position = "bottom", legend.title = element_blank())  # then we modify the legend
p  # and, finally, we plot the object
```

```{r}
#Scatterplot for Gender versus Weight
p <- ggplot(data = d, aes(x = gender, y = weight, 
    color = factor(gender)))  # first, we build a plot object and color points by Family
p <- p + xlab("Gender") + ylab("Height")  # then we modify the axis labels
p <- p + geom_point()  # then we make a scatterplot
p <- p + theme(legend.position = "bottom", legend.title = element_blank())  # then we modify the legend
p  # and, finally, we plot the object
```

```{r}
#Scatterplot for Gender versus Weight
p <- ggplot(data = d, aes(x = gender, y = weight, 
    color = factor(gender)))  # first, we build a plot object and color points by Family
p <- p + xlab("Gender") + ylab("Age")  # then we modify the axis labels
p <- p + geom_point()  # then we make a scatterplot
p <- p + theme(legend.position = "bottom", legend.title = element_blank())  # then we modify the legend
p  # and, finally, we plot the object
```


#Problem 4
#Q-Q Historgrams and Looking for Normality